Post-Shock Transition Estimation

### 2021-03-16 problem_statement.tex
made comments to problem statement

\bibliographystyle{plainnat}

@@

@@

@@

Suppose at $t=T_i^*$, one knows the shock is about to occur at $t=T_i^*+1$. Consider the following model
\begin{align*}
  \mc{M} \colon 
  \begin{array}{l}
    y_{i,t} = \eta_i +  \alpha_{i,t}I(t > T_i^*)+ \phi_i y_{i,t-1} + \mathbf{x}_{i,t}\bs{\theta}_i + \varepsilon_{i,t}\\[.3cm]
    \alpha_{i,t} = \mu_{\alpha} + \mbf{x}_{i, t}\boldsymbol{\delta}_i + \tilde{\varepsilon}_i
  \end{array},
\end{align*}
where $D_{i,t}= I(t= T_i^* +t)$, $I(\cdot)$ is an indicator function, and $\mbf{x}_{i,t}, \boldsymbol{\theta}_{i}\in \reals^p$ with $p\geq 1$. The random effects structure is oragnized as below.
\begin{align*}
  \tilde{\varepsilon}_i &\simiid \mc{F}_{\tilde{\varepsilon}} \text{ with } \E_{\mc{F}_{\tilde{\varepsilon}}}, \Var_{\mc{F}_{\tilde{\varepsilon}}}(\tilde{\varepsilon}_i)= \sigma^2_{\alpha}  >0 \\
  \eta_i & \indep \alpha_{i,t} \indep \phi_i \indep \boldsymbol{\theta}_i \indep \varepsilon_{i,t} \indep \tilde{\varepsilon}_i.
\end{align*}
The candidate forecasts are
\begin{align*}
  &\text{Forecast 1}: \hat{y}_{1,T_1^*+k + j}^{(1)} = \hat\eta_1 
    + \hat\phi_1 \hat{y}^{(1)}_{1,T_1^*+k+j-1} + \mbf{x}_{1,T_1^*+k+j-1} \hat{\bs{\theta}}_1
    , \\
  &\text{Forecast 2}: \hat{y}_{1,T_1^*+k+j}^{(2)} = \hat\eta_1 
    + \hat\phi_1 \hat{y}^{(2)}_{1,T_1^*+k+j-1} + \mbf{x}_{1,T_1^*+k+j-1} \hat{\bs{\theta}}_1
    + \hat{\alpha}^{(j)},
\end{align*}
where $\hat{y}_{1, T_1^*}^{(1)}=\hat{y}_{1, T_1^*}^{(2)}=y_{1,T_1^*}$, $\hat{\alpha}^{(j)}$ is an estimate of the shock effect occurring in the model of $y_{1,T_1^*+k+j}$, and other parameters are estimated in an unbiased fashion, e.g., OLS. Define
\begin{align}
  \begin{array}{lll}
     \Theta &= &\{(\eta_i, \phi_i, \bs{\theta}_i, \alpha_{i,t}, \mbf{x}_{i,t}, y_{i,t-1}, \bs{\delta}_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
    \Theta_1 &= &\{(\eta_i, \phi_i, \bs{\theta}_i, \alpha_{i,t}, \mbf{x}_{i,t}, y_{i,t-1}, \bs{\delta}_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
  \end{array}
\end{align}

@@

@@

\bibliography{synthetic-prediction-notes}

>>>>

\newenvironment{commentline}[1]{
\noindent{\color{red} \rule{\linewidth}{0.5mm}}
\textbf{Comment}: #1

\noindent{\color{red} \rule{\linewidth}{0.5mm}}
}

@@

\commentline{Do not use `he', use something like `the researcher'.}

@@

\commentline{Our method is not synthetic control, it's a weighted-adjustment estimator that is inspired by synthetic control.}

@@

Suppose at $t=T_i^*$, one knows the shock is about to occur at $t=T_i^*+1$. Consider the following model
\begin{align*}
  \mc{M} \colon 
  \begin{array}{l}
    y_{i,t} = \eta_i +  \alpha_{i,t}I(t > T_i^*)+ \phi_i y_{i,t-1} + \mathbf{x}_{i,t}\bs{\theta}_i + \varepsilon_{i,t}\\[.3cm]
    \alpha_{i,t} = \mu_{\alpha} + \mbf{x}_{i, t}\boldsymbol{\delta}_i + \tilde{\varepsilon}_i
  \end{array},
\end{align*}
where $D_{i,t}= I(t= T_i^* +t)$, $I(\cdot)$ is an indicator function, and $\mbf{x}_{i,t}, \boldsymbol{\theta}_{i}\in \reals^p$ with $p\geq 1$. The random effects structure is organized as below.
\begin{align*}
  \tilde{\varepsilon}_i &\simiid \mc{F}_{\tilde{\varepsilon}} \text{ with } \E_{\mc{F}_{\tilde{\varepsilon}}} = 0, \Var_{\mc{F}_{\tilde{\varepsilon}}}(\tilde{\varepsilon}_i)= \sigma^2_{\alpha}  >0, \\
  \eta_i & \indep \alpha_{i,t} \indep \phi_i \indep \boldsymbol{\theta}_i \indep \varepsilon_{i,t} \indep \tilde{\varepsilon}_i.
\end{align*}
The candidate forecasts are
\begin{align*}
  &\text{Forecast 1}: \hat{y}_{1,T_1^*+k + j}^{(1)} = \hat\eta_1 
    + \hat\phi_1 \hat{y}^{(1)}_{1,T_1^*+k+j-1} + \mbf{x}_{1,T_1^*+k+j-1} \hat{\bs{\theta}}_1
    , \\
  &\text{Forecast 2}: \hat{y}_{1,T_1^*+k+j}^{(2)} = \hat\eta_1 
    + \hat\phi_1 \hat{y}^{(2)}_{1,T_1^*+k+j-1} + \mbf{x}_{1,T_1^*+k+j-1} \hat{\bs{\theta}}_1
    + \hat{\alpha}^{(j)},
\end{align*}
where $\hat{y}_{1, T_1^*}^{(1)}=\hat{y}_{1, T_1^*}^{(2)}=y_{1,T_1^*}$, $\hat{\alpha}^{(j)}$ is an estimate of the shock effect occurring in the model of $y_{1,T_1^*+k+j}$, and other parameters are estimated in an unbiased fashion, e.g., OLS.

\commentline{There is also the h-ahead forecast model, see: \url{https://www.ssc.wisc.edu/~bhansen/papers/hstep.pdf} Perhaps their framework is more appropriate. See a more authoritative presentation in \cite{clements1996multi}.}

Define
\begin{align}
  \begin{array}{lll}
     \Theta &= &\{(\eta_i, \phi_i, \bs{\theta}_i, \alpha_{i,t}, \mbf{x}_{i,t}, y_{i,t-1}, \bs{\delta}_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
    \Theta_1 &= &\{(\eta_i, \phi_i, \bs{\theta}_i, \alpha_{i,t}, \mbf{x}_{i,t}, y_{i,t-1}, \bs{\delta}_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}
  \end{array}
\end{align}

@@

\commentline{We could consider an $h$-ahead forecasting procedure at each value over some window $h = 1,\ldots,H$. We can then consider the adjusted and unadjusted responses at every $h$, and then develop a test of the differences between these two quantities for each $h$. Alternatively, we could consider if the shock effect washes out in each series in the donor pool for each $h$. Both of these procedures would require a multiple testing framework. All of this may depend on the forecast horizon $H$. }

@@

\commentline{The $h$ ahead framework does not involve $x$ values beyond the range of data collection. We could do something with forecasting, but that seems shaky.}

\bibliographystyle{plainnat}
\bibliography{synthetic-prediction-notes}
